Teaching a Class to Grade Itself using Game Theory

### 2013-09-17 Primes Write up.tex
Added chart
Changed bibliography to bibtex and added all the neccesary information, might change format later

\documentclass[12pt, Arial]{article}   	
\title{Teaching a Class to Grade Itself using Game Theory}
\author{Nick Kaashoek and William Wu}
\date{\today}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started~\cite{canmoocsreducecc}. However, the MOOC's main importance comes from its scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

@@

\section{Improved Verification Mechanism}
The major change made in this mechanism was one to assumption number 11. Now assumption 11 reads as follows:
\emph{All students are able to communicate with each other}

@@

\begin{thebibliography}{9}

\bibitem{canmoocsreducecc}
  % http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
  Ruth, S. (2012). \emph{Can MOOCs and existing e-learning paradigms help reduce college costs}? International Journal of Technology in Teaching and Learning, 8(1), 21-32.

\bibitem{makingsenseofmoocs}
  % http://www-jime.open.ac.uk/jime/article/viewArticle/2012-18/html
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{swotanalysisofmoocs}
  % http://www.editlib.org/p/112020
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{rightandwrongmoocs}
  % http://www.tonybates.ca/2012/08/05/whats-right-and-whats-wrong-about-coursera-style-moocs/
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{boycottfinal}
  % http://www.insidehighered.com/news/2013/02/12/students-boycott-final-challenge-professors-grading-policy-and-get
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{autograding}
  % http://www.ecu.edu/cs-acad/fsonline/customcf/committee/tg/2013proposals/08.pdf
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{edxsoftware}
  % http://www.bostonmagazine.com/news/blog/2013/04/04/edx-now-has-robots-to-grade-your-essays/
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{automatedsystemssuck}
  Herrington, A., \& Moran, C. (2012). \emph{Writing to a machine is not writing at all}. In N. Elliot \& L. Perelman (Eds.), Writing assessment in the 21st century: Essays in honor of Edward M. White (pp. 219-232). New York, NY: Hampton Press.

\bibitem{howaccurateispeergrading}
  % http://educationgroup.mit.edu/HHMIEducationGroup/wp-content/uploads/2011/05/Freeman-et-al-2010.pdf
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{theproblemswithpeergradingincoursera}
%http://www.insidehighered.com/blogs/hack-higher-education/problems-peer-grading-coursera
Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{robogradingproblems}
%http://bltnotjustasandwich.com/2013/04/05/the-problems-with-moocs-1-robo-essay-grading/
Author,
  \emph{Title}.
  Source,
  Year.

\end{thebibliography}
\end{document}

>>>>

\documentclass[12pt, Arial]{article}   	
\title{Teaching a Class to Grade Itself using Game Theory}
\author{Nick Kaashoek and William Wu}
\date{\today}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{cite}
\usepackage{graphicx}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
\cite{m85}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started~\cite{canmoocsreducecc}. However, the MOOC's main importance comes from its scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

@@

\section{Improved Calibration Mechanism}
The major change made in this mechanism was one to assumption number 11. Now assumption 11 reads as follows:
\emph{All students are able to communicate with each other}

@@

\section{Illustrations}
{
\noindent
\includegraphics[width=\textwidth]{Chart.eps}
}
\bibliography{bibliography}{}
\bibliographystyle{plain}
\end{document}
